A Quantitative Genetic Linked Selection Model fit to the Negative Selection Process in Humans

### 2023-07-05 manuscript/manuscript.tex
ms changes

However, across all of our annotation models, new deleterious mutations in
putatively conserved features are consistently estimated to have strongly
deleterious effects (Figure \ref{fig:figure-3}A). This includes features such
as coding sequences, PhastCons regions, or the top 6\% of basepairs with the
most pathogenic CADD scores. Thus, even with a model that can better
distinguish weak versus strong selection, our DFE estimates suggest

>>>>

However, across all of our annotation models, new deleterious mutations in
likely conserved features are consistently estimated to have strongly
deleterious effects (Figure \ref{fig:figure-3}A) consistent with previous work
\parencite{McVicker2009-ax,Murphy2022-sj}. This includes features such as
coding sequences, PhastCons regions, or the top 6\% of basepairs with the most
pathogenic CADD scores. However, we find that there is considerable uncertainty
in how strong selection is against the most deleterious mutations. For example,
in the CADD 6\% full-track model, new mutations are estimated to have a
selection coefficients of $s = 10^{-1}$ with 42\% chance, $s=10^{-2}$ with
7.8\% chance, and $s=10^{3}$ with 41\% chance. These estimates suggest a
bimodal DFE (Figure \ref{fig:figure-3}A, second row, left column), and are
mirrored across the other CADD models.

Given that previous methods have typically not estimated the DFE up to
selection coefficients of $s=10^{-1}$, we ran additional models using a DFE
constrained to $s=10^{-2}$. Each of these constrained-DFE models across all
populations fit the data less well than models run with the grid up to
$s=10^{-1}$, explaining 1\% less of the leave-one-chromosome-out variation on
average. As expected, the constrained-DFE models put more mass on $s=10^{-2}$
(see Supplementary Table \ref{supp:tbl-r2}).

Our method's estimates for the DFE rely on a
pre-specified logarithmic grid; we use a fairly fine-scale grid from $10^{-8}$
to $10^{-1}$.

Across the CADD models, we note a discontinuity in DFE estimates,
where the largest mass is placed on the strongest selection coefficient ($s =
10^{-1}$), very little on the next coefficient ($s=10^{-2}$), and mo($\approx
41\%-67\%$)

These DFE estimates also suggest that our method
can accurately estimate when regions are under weak or no constraint.

Across our full-coverage models, the estimated DFE for the ``other" feature
containing the rest of the genome is estimated to nearly 100\% neutral
($s=10^{-8}$). In some cases (e.g. the CADD 6\% and 8\% models) the ``other"
estimates a small fraction ($\approx 3\%-5\%$) of mutations in the ``other"
region have a strongly deleterious impact ($s=10^{-1}$). This is likely due to
non-identifiability between $\pi_0$ and a small chance of deleterious mutations
occurring on the unannotated remainder of the genome.

Our DFE estimates

Thus, even though our model can better distinguish
weak versus strong selection, our DFE estimates suggest
